Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-13 doc/manuscript/manuscript.Rmd
add notes for future zhian

Each isolate was regenerated by activating one or several sclerotia according to the method described previously [@matheron1989in-vitro].
Once actively growing, mycelial compatibility group (MCG) and aggressiveness was determined for each isolate.
MCG was determined through co-culturing isolates in pairs on potato-dextrose agar (PDA) plates, where incompatibility of different MCGs resulted in formation of a mycelial barrier or barrage line [@kohn1990mycelial].
Since MCGs are considered mutually exclusive, pairing was not required between all isolates in the study.

@@

In this study, we characterized the diversity of *Sclerotinia sclerotiorum* from dry bean fields across the United States.
Our results suggest that populations from white mold nurseries may reflect the populations of the surrounding regions. 
We found significant population differentiation by geographic region, mainly differentiated into four broad groups, a Coastal Region, Midwestern Region, International Region, and Mexico. 
There were not significant associations between multilocus genotypes and mycelial compatibility groups.

>>>>

Each isolate was regenerated by activating one or several sclerotia according to the method described previously [@matheron1989in-vitro].
Once actively growing, mycelial compatibility group (MCG) and aggressiveness was determined for each isolate.
MCG was determined as described in @otto-hanson2011variation through co-culturing isolates in pairs on potato-dextrose agar (PDA) plates, where incompatibility of different MCGs resulted in formation of a mycelial barrier of dead tissue (barrage line) [@kohn1990mycelial].
Since MCGs are considered mutually exclusive, pairing was not required between all isolates in the study.

@@

<!-- 
 - Big Picture reminder of importance
   + This is an extension of a previous work [@otto-hanson2011variation]
   + White Mold Nurseries serve as good way to screen potential resistant lines, avoiding environmental effects
   + It's unclear how genetic structure can influence
 - Critical Analysis of Major Findings
   + This is the largest genetic analysis of *S. sclerotiorum* to date
   + Similar to the findings of @otto-hanson2011variation, we found that
     Region has a strong influence on both population structure and
     severity.
   + North Dakota appeared
 - Additional Findings and how they fit into the literature
 - Limitations
 - Future Directions
 - Overall Conclusion and Impact
-->

In this study, we characterized the diversity of *Sclerotinia sclerotiorum* from dry bean fields across the United States.
Our results suggest that, in general, populations from white mold nurseries reflect the populations of the surrounding regions. 
We found significant population differentiation by geographic region, mainly differentiated into four broad groups, a Coastal Region, Midwestern Region, International Region, and Mexico. 
We found no significant associations between genotype and phenotype.
